HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex
ww

\com{
In Figure~\ref{mttool} you we show the MT evaluation tool. The sentence at the top shows the complete MT system output. Underneath the MT output is the  source sentence.  Underneath the source sentence we see its expandable semantic tree structure with both lexical and structural nodes. Lexical nodes only have traffic light annotation, whereas a structural node would normally be labelled ``A'' or ``B'' but could also be labelled as a lexical node, in the case where there is no word to word correspondence for the translation of its children.

@@

\subsection{UCCA Annotation}
Source sentences are all in English, and the UCCA annotation was performed by four
computational linguists\oa{were there no other annotators from Prague? Ondrej
does not remember! Was it just Ondrej+Jana Sindlerova? Then it would be one
computer scientist and one linguist for Czech.}.

@@

For each of the four language pairs under consideration  we built phrase-based MT systems
using Moses \cite{Koehn:2007}. We used large training sets extracted from OPUS \cite{tiedemann:2009}, and
the data sets released for the WMT14 medical translation task \cite{bojar-EtAl:2014:W14-33}, to provide between
45 and 85 million sentences of training data, depending on language pair\oa{I think we should probably
  say how much in each.}.

@@

In order to assess the consistency of the annotation, we measure the Inter-Annotator
Agreement (IAA) using Cohen's Kappa on the multiply-annotated portions of the data.
For German, Polish and Romanian we used two annotators, with a significant overlap
between the sentences they annotated. For Czech we had one main annotator, plus
several second annotators, so we treat all these second annotators as a single
annotator.

To calculate Kappa, we consider the annotation task as a classification task on 
nodes, and consider those nodes which have two annotations from different
annotators.
We report the overall Kappa, as well as separate Kappas on lexical
nodes (annotated as red, orange or green) and the structural nodes (annotated
as acceptable or bad). In general there should not be confusion between the two
types of nodes, and in future work the separation between the nodes should be enforced
by the tool.  The Kappas are shown in \tabref{tab:iaa}
\begin{table}[!ht]
\begin{center}
\begin{tabular}{l|cccc}
 & cs & de & pl & ro \\
\hline
Sentences & 181 & 102 & 334 & 217 \\
\hline
All nodes & 4686   & 2793   & 8384   & 5604  \\
Kappa & 0.64   & 0.61   & 0.58   & 0.69  \\
\hline
Lexical nodes & 2982 & 1724 & 5386 & 3570 \\
Kappa & 0.54 & 0.29 & 0.54 & 0.50 \\
\hline
Structural nodes & 1602 & 1040 & 2655 & 1989 \\
Kappa & 0.31 & 0.44 & 0.33 & 0.58 \\
\end{tabular}
\caption{Inter-annotator agreement for the multiply-annotated portions of the data, as
measured by Cohen's Kappa. }
\label{tab:iaa}
\end{center}
\end{table}

@@

}
\end{tabular}
\caption{Inter-annotator Agreement (Kappa) versus sentence length, separately for
structural and lexical nodes. The numbers are the node counts in each bin. }
\label{fig:iaalength}
\end{figure*}

@@

We see from \figref{fig:iaalength} that there is no reduction of IAA with sentence
length, except perhaps in German. Also, from \tabref{tab:iaa} the overall IAA
is quite similar (0.6-0.7) for all languages, showing good agreement, but there are
differences observed when we break down by node type.  In particular, we see a contrast  between
Czech and Polish (where the IAA is higher for lexical nodes than structural nodes) and German and Romanian
(where the reverse  is true). We also observe low IAA (around 0.3) in some cases, for instance 
in German lexical nodes, and for Polish and Czech structural nodes.

>>>>

\com{
In Figure~\ref{mttool} you we show the MT evaluation tool. The sentence at the top shows the complete MT system output. Underneath the MT output is the  source sentence.  Underneath the source sentence we see its expandable semantic tree structure with both lexical and structural nodes. atomic nodes only have traffic light annotation, whereas a structural node would normally be labelled ``A'' or ``B'' but could also be labelled as a lexical node, in the case where there is no word to word correspondence for the translation of its children.

@@

\subsection{UCCA Annotation}
Source sentences are all in English, and the UCCA annotation was performed by four
computational linguists and one linguist.

@@

For each of the four language pairs under consideration  we built phrase-based MT systems
using Moses \cite{Koehn:2007}. We used large training sets extracted from OPUS \cite{tiedemann:2009}, and
the data sets released for the WMT14 medical translation task \cite{bojar-EtAl:2014:W14-33}, to provide between
45 and 85 million sentences of training data, depending on language pair\oa{I think we should probably
  say how many in each.}.

@@

In order to assess the consistency of the annotation, we measure the Inter-Annotator
Agreement (IAA) using Cohen's Kappa on the multiply-annotated portions of the data.
For German, Polish and Romanian we used two annotators, with a significant overlap
between the sentences they annotated. For Czech we had one main annotator, who
annotated the entire batch, as well multiple secondary annotators, where
each annotated a sub-part of the batch. \oa{i editted it. is what i wrote correct?}

In order to compute Kappa, we consider the annotation task as a classification task on 
nodes, and compute agreement on nodes which have two annotations from different annotators.
We report the overall Kappa, as well as separate Kappas on atomic
nodes (annotated as Red, Orange or Green) and the structural nodes (annotated
as Adequate or Bad). In general there should be little confusion between the two
types of nodes, and in future work the separation between the nodes should be enforced
by the tool\oa{but there may be some disagreement in the margins on what nodes are atomic and
  what are not}. The Kappas are shown in \tabref{tab:iaa}.

\begin{table}[!ht]
\begin{center}
\begin{tabular}{l|cccc}
 & cs & de & pl & ro \\
\hline
Sentences & 181 & 102 & 334 & 217 \\
\hline
All nodes & 4686   & 2793   & 8384   & 5604  \\
Kappa & 0.64   & 0.61   & 0.58   & 0.69  \\
\hline
Atomic nodes & 2982 & 1724 & 5386 & 3570 \\
Kappa & 0.54 & 0.29 & 0.54 & 0.50 \\
\hline
Structural nodes & 1602 & 1040 & 2655 & 1989 \\
Kappa & 0.31 & 0.44 & 0.33 & 0.58 \\
\end{tabular}
\caption{Inter-annotator agreement for the multiply-annotated portions of the data, as
measured by Cohen's Kappa. }
\label{tab:iaa}
\end{center}
\end{table}

@@

}
\end{tabular}
\caption{Inter-annotator Agreement (Kappa) versus sentence length, separately for
structural and atomic nodes. The numbers are the node counts in each bin. }
\label{fig:iaalength}
\end{figure*}

@@

We see from \figref{fig:iaalength} that there is no reduction of IAA with sentence
length, except perhaps in German. Also, from \tabref{tab:iaa} the overall IAA
is quite similar (0.6-0.7) for all languages, showing good agreement.
However, there are differences observed when we break down by node type.
In particular, we see a contrast  between
Czech and Polish, where the IAA is higher for atomic than for structural nodes, and German and Romanian,
where the reverse is true. We also observe low IAA (around 0.3) in the cases of
German atomic nodes, and Polish and Czech structural nodes.
